Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-03-19 docs/ms.tex
Update ms.tex

This paper is organized as follows...

>>>>

How it's related to galaxy -galaxy lensing
In galaxy - galaxy lensing what people usually do is stack many lensing signals together and get the "average"
shear map,and then infers the mean mass profile of galaxy or galaxy cluster.
However with HB method we can calculate the posterior distribution of mass profile of each lens and propagate all the uncertainty
from to the posterior distributions.
This paper is organized as follows...
